
\cvsection{Education}

\begin{cventries}

  \cventry
    {PhD in Computer Science} % Degree
    {University of Cambridge} % Institution
    {Cambridge, UK} % Location
    {Oct. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Focus:} Probabilistic Machine Learning. Supervised by Prof. Neil Lawrence and funded by the Accelerate Programme for Scientific Discovery.}
      \end{cvitems}
    }

  \cventry
    {MPhil in Management} % Degree
    {University of Cambridge} % Institution
    {Cambridge, UK} % Location
    {Oct. 2016 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Commendation (70\%). \textbf{Focus:} Strategic Valuation (top prize), Economics. \textbf{Audits:} Measure Theory, Philosophy of Science, Physics.}
        \item {Jaguar Land Rover consulting project: Modeled the contribution of JLR to the UK economy in a highly collaborative setting. Conducted \textbf{original research} on improving the accuracy of input-output multipliers. Highly commended for the work and presentation.}
        \item {Coloplast Internship (Aug. '17): Aided implementation of a time series forecasting model (involving splines, linear filters and ARIMA error processes) and automated model fitting.}
      \end{cvitems}
    }

  \cventry
    {BSc Hons in Actuarial Science, \textbf{Statistics Major}} % Degree
    {Heriot-Watt University} % Institution
    {Edinburgh, UK} % Location
    {Sep. 2013 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Awards:} Distinction (83\%) (top 3\%), CT1-8, Volunteering - Bronze (ChessSoc President, Student Union Exec, Mentor). Obtained BSc at age 18.}
        \item {\textbf{Focus:} Statistics, Quantitative Risk Management, Mathematical Finance. \textbf{Project Areas:} GARCH models, copulas, extreme value theory, stochastic calculus, liquidity risk, economic scenario generators and advanced statistical inference. Published in the actuarial magazine.}
      \end{cvitems}
    }

  \vspace{-5mm}

\end{cventries}
