
\cvsection{Experience}

\begin{cventries}

  \cventry
    {Quant Analyst + Developer, AVP} % Job title
    {Barclays} % Organization
    {London, UK} % Location
    {Dec. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and implementing large-scale statistical models for forecasting the evolution of portfolio balances, accounting for individual behavior. I'm responible for the modelling of certain portfolios - term deposits, loans, wealth, savings and mortgage applications, mainly using markovian models, regularised and hierarchical GLMs, GAMs and models involving time series.}
        \item {In three cases (involving data cleaning, data structure manipulation and Monte Carlo simulation), reduced execution time of critical model components from days to seconds using Spark and C++.}
      \end{cvitems}
    }

  \cventry
    {Data Scientist + Statistician} % Job title
    {Sciemus} % Organization
    {London, UK} % Location
    {Sep. 2017 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Was involved with building and maintaining end-to-end stats/tech related solutions, particularly in the space, weather and power business areas. This involved data cleaning, analysis, modelling, documentation, web-app development and deployment, basic server and database maintenance, research and development of infrastructure (e.g. aiding development of a distributed computing cluster on AWS).}
        \item {On the modelling side, I’ve worked with GLMs for assessing risk probabilities, Hidden Markov models \& sparse Gaussian Processes to model rates based on large-scale weather data, simple random fields in the form of CNNs to model rainfall data, importance sampling \& subset simulation to accelerate simulations, fuzzy logical risk models, basic prior elicitation \& associated Jacobian adjustments.}
      \end{cvitems}
    }

  \cventry
    {Data Science Intern} % Job title
    {Coloplast} % Organization
    {Peterborough, UK} % Location
    {Jul. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Aided implementation of a seasonal time series forecasting model. Introduced loss functions, splines and linear filters to the implementation, linked model components, fit an ARMA model to the resultant error series and automated model fitting.}
      \end{cvitems}
    }

  \cventry
    {Quant Management Consultant} % Job title
    {Jaguar Land Rover} % Organization
    {Cambridge, UK} % Location
    {May. 2017 - Jun. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Modelled the contribution of Jaguar Land Rover to the UK economy in a highly collaborative setting. Conducted \textbf{original research} on improving the accuracy of multipliers within input-output theory by utilizing internal supply chain data. Highly commended for the work and presentation.}
      \end{cvitems}
    }

\end{cventries}
